Composition-climate paper

### 2015-04-13 Composition_Ecology.Rmd
Should mostly be local changes that don't need to be resolved. . .
Added `gridExtra` to the list of loaded packages.
Big changes to `resampling_climate`, removed early text blobs, incuding `landuse` section.
* Moved `hellinger` function to new file.
* removed the need for a spatial points object in `get_dens_era`
* turned off text output in the bit `data.table` `ldply`.
* removed a whole huge chunk of code to make things easier to do.

```{r, fig.width=5}
# Load climate data and generate the pre-sett and modern bounds:
#  Pre-settlement climate: 1900 - 1930
#  Modern climate: 1960 - 1990

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_fia.R')     # gives agg.dens
source('R/load_ncdf.R')    # gives western and eastern

@@

Results
---------------
Across the region PLS cells account for X

>>>>

```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Load climate data and generate the pre-sett and modern bounds:
#  Pre-settlement climate: 1900 - 1930
#  Modern climate: 1960 - 1990

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')

@@

Results
---------------
The Public Lands data is spatially extensive, sampling occured across the region in a regular pattern, while the FIA is limited to regions with forest cover.  As such, the extent of points is not overlapping.  Add to this the extensive forest cover change in the region and we see significant changes in cover between FIA and PLS data.

```{r loss_gain_fig, warning=FALSE, message=FALSE, echo=FALSE}

source('R/figures/gain_loss_plot.R')

```
**Figure 1**.  *Gain loss and continuous presence for PLSS and FIA tree taxa.*

The shifts in distribution to lead to changes in the apparent climate envelopes of the taxa, but these are dwarfed by the shifts in regional climate across the area.
```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}

source('R/resampling_climate.R')
source('R/figures//climate_boxplots.R')

Whe we examine the taxa seperately we can see that by far the majority of comparisons show greater differences due to climate change than due to shifts in distribution:

```{r climate_shifts, warning=FALSE, message=FALSE, echo=FALSE}

source('R/hellinger_dists.R')

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point() + geom_abline(intercept=0, slope = 1) + facet_wrap(~shift) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw()

This plot makes it clear that precipitation across the region has changed significantly since the PLS era (or the early 1900s), while overall $t_{mean}$ has changed less.  Among taxa only beech, ironwood, hemlock, fir and tamarak show distributional changes larger than the effect of shifting climate.  For beech, a shift is seen in $t_{mean}$, where $t_{mean}$ for the PLS era distribution is 6.8^o^C, but is lower for the FIA distribution using PLS era climate, at $t_{mean}$ = 6.6^o^C.  This is likely due to a northward shift in beech distribution in the current FIA dataset due to the loss of southern beech forests (earlier Figure).
